 

### 2021-01-11 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Leaf traits are shaped on the basis of light and height and show different degrees of foliar plasticity in accordance with the intensity and availability of light which also optimize water uptake, heat and C uptake by leaves across forest vertical strata. After the formation of leaves to integrated light, it takes 30-60 days for traits to stabalize in woody and herbaceous species [@niinemetsLeafAgeDependent2016a]. A network of sensory photoreceptors in leaves such as phytochromes among others mediate response to PAR, and ratio of red to far red radiation [R:FR] falling on the surface. This enables acclimation or avoidance response through development of necessary traits [Casal, 2013]. As a result, degrees of high irradiance gives rise to variations of sun-leaf traits  compared to degrees of low irradiance-- characterized by shade-- shapes variations of shade-leaf traits [@poorterMetaanalysisPlantResponses2019b; Sack et al 2006], which ultimately also shapes leaf structural, chemical and physiological traits as well [Keenan and Niinemets et al. 2016].

>>>>

Leaf traits are shaped on the basis of light and height and show different degrees of foliar plasticity in accordance with the intensity and availability of light which also optimizes water uptake, heat and C uptake by leaves across forest vertical strata. After the formation of leaves to integrated light, it takes 30-60 days for traits to stabalize in woody and herbaceous species [@niinemetsLeafAgeDependent2016a]. A network of sensory photoreceptors in leaves such as phytochromes among others mediate response to PAR, and ratio of red to far red radiation [R:FR] falling on the surface. This enables acclimation or avoidance response through development of necessary traits [Casal, 2013]. As a result, degrees of high irradiance gives rise to variations of sun-leaf traits  compared to degrees of low irradiance-- characterized by shade-- shapes variations of shade-leaf traits [@poorterMetaanalysisPlantResponses2019b; Sack et al 2006], which ultimately also shapes leaf structural, chemical and physiological traits as well [Keenan and Niinemets et al. 2016].
